---
title: "Living systematic reviews - applying ML to classify new preprints uploaded to medRxiv"
subtitle: ""
author: "<br/> Luke McGuinness <br/> + Lena Schmidt"
institute: "University of Bristol"
date: "`r format(Sys.Date(), format = '%d/%m/%Y')`"
output:
  xaringan::moon_reader:
    css: ["default", "reports/my-theme.css"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

``` {r, echo = FALSE}

cache <- TRUE

```

# Session overview

.large[

* Introduction

* Extracting the data

* Applying the model
  
* Initial results

* Discussion

]


---
class: inverse, center, middle

# Introduction

---

# Living systematic reviews

.larger[An LSR is “<i>a systematic review that is continually updated, incorporating relevant new evidence as it becomes available</i>” <sup>1,2</sup>

Require continuous searching of the literature to identify new relevant studies.



]

.footnote[

<sup>1</sup> <i>Guidance for the production and publication of Cochrane living systematic reviews: Cochrane Reviews in living mode Cochrane.</i> Version: December 2019  
<sup>2</sup> Elliott JH, Synnot A, Turner T, Simmonds M, Akl EA, McDonald S, et al. <i>Living systematic review: 1. Introduction-the why, what, when, and how.</i> Journal of Clinical Epidemiology. 2017;91:23-30.

]


---

# Living systematic reviews

Most commonly used search frequency is monthly


---

# Extracting the data


``` {r, echo = FALSE, cache = cache}
library(stringr)
library(here)
library(pushoverr)
library(rvest)

page <- read_html("https://www.medrxiv.org/search/%252A")

results <- page %>%
  html_nodes("#page-title") %>%
  html_text()

results <- as.numeric(word(results))

```

<i> medRxiv </i> is the new preprint repostiory for the medical, clinical, and related health sciences.

 which currently contains `r results` preprints


---

# Extracting the data

Negotiation
